The SMT Competition 2015--2018

### 2019-03-16 2018/report/table-winners-main.tex
No solvers were entered into QF_ABVFP in 2017
Nicer tables (using the booktabs package)
Removed old main track winners table.

\scalebox{.84}{\begin{tabular}{|rcccc|}
\hline

@@

\hline
%\multicolumn{1}{l}{}            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                  \\ \cline{5-5}
ABVFP                            & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
\multicolumn{1}{|r|}{ALIA}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
AUFBVDTLIA                       & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{4-5}
AUFDTLIA                         & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5}
\multicolumn{1}{|r|}{AUFLIA}     & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
\multicolumn{1}{|r|}{AUFLIRA}    & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
\multicolumn{1}{|r|}{AUFNIRA}    & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{Vampire}                                        & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
\multicolumn{1}{|r|}{BV}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Q3B}            & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
BVFP                             & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{5-5}
FP                               & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
\multicolumn{1}{|r|}{LIA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
\multicolumn{1}{|r|}{LRA}        & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
\multicolumn{1}{|r|}{NIA}        & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
\multicolumn{1}{|r|}{NRA}        & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Vampire}        & \multicolumn{1}{c|}{Redlog}   & \multicolumn{1}{c|}{{[}Z3{]}/Vampire} \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_ABV}    & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5}
QF\_ABVFP                        & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_ALIA}   & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_ANIA}   & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_AUFBV}  & \multicolumn{3}{c|}{{[}MathSAT{]}}                                                                  & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_AUFLIA} & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_AUFNIA} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_AX}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_BV}     & \multicolumn{2}{c|}{Boolector}                                      & \multicolumn{2}{c|}{Boolector/MinkeyRink}                             \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_BVFP}   & \multicolumn{1}{c|}{Z3}       & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
QF\_DT                           & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_FP}     & \multicolumn{1}{c|}{Z3}       & \multicolumn{1}{c|}{{[}MathSAT{]}}  & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{COLIBRI}          \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_IDL}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_LIA}    & \multicolumn{3}{c|}{{[}MathSAT{]}}                                                                  & \multicolumn{1}{c|}{SPASS-SATT}       \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_LIRA}   & \multicolumn{2}{c|}{Yices2}                                         & \multicolumn{2}{c|}{{[}Z3{]}}                                         \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_LRA}    & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_NIA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_NIRA}   & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{2}{c|}{SMT-RAT}                                          \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_NRA}    & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{1}{c|}{Yices2}   & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_RDL}    & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
QF\_SLIA                         & \multicolumn{1}{l}{}          & \multicolumn{1}{l}{}                & \multicolumn{1}{l|}{}         & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UF}     & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFBV}   & \multicolumn{4}{c|}{Boolector}                                                                                                              \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFIDL}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFLIA}  & \multicolumn{2}{c|}{{[}Z3{]}}                                       & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFLRA}  & \multicolumn{4}{c|}{Yices2}                                                                                                                 \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFNIA}  & \multicolumn{1}{c|}{CVC4}     & \multicolumn{1}{c|}{Yices2/CVC4}    & \multicolumn{2}{c|}{Yices2}                                           \\ \cline{2-5}
\multicolumn{1}{|r|}{QF\_UFNRA}  & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}         & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{1}{c|}{Yices2}           \\ \cline{2-5}
\multicolumn{1}{|r|}{UF}         & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{Vampire}  & \multicolumn{1}{c|}{CVC4/Vampire}     \\ \cline{2-5}
\multicolumn{1}{|r|}{UFBV}       & \multicolumn{4}{c|}{{[}Z3{]}}                                                                                                               \\ \cline{2-5}
UFDT                             & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{2}{c|}{CVC4}                                             \\ \cline{4-5}
UFDTLIA                          & \multicolumn{1}{l}{}          & \multicolumn{1}{l|}{}               & \multicolumn{1}{c|}{Vampire}  & \multicolumn{1}{c|}{CVC4}             \\ \cline{2-5}
\multicolumn{1}{|r|}{UFIDL}      & \multicolumn{1}{c|}{{[}Z3{]}} & \multicolumn{2}{c|}{CVC4}                                           & \multicolumn{1}{c|}{{[}Z3{]}}         \\ \cline{2-5}
\multicolumn{1}{|r|}{UFLIA}      & \multicolumn{4}{c|}{CVC4}                                                                                                                   \\ \cline{2-5}
\multicolumn{1}{|r|}{UFLRA}      & \multicolumn{1}{c|}{CVC3}     & \multicolumn{3}{c|}{{[}Z3{]}}                                                                               \\ \cline{2-5}
\multicolumn{1}{|r|}{UFNIA}      & \multicolumn{1}{c|}{CVC4}     & \multicolumn{2}{c|}{Vampire}                                        & \multicolumn{1}{c|}{{[}Z3{]}/Vampire} \\ \hline

>>>>

\scalebox{.83}{%
\renewcommand{\arraystretch}{1.01}%
  \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
\toprule
\rc

@@

\hline \hline
\cc ABVFP        & \cc             & \cc             & \cc                    & \cc {CVC4} *          \\
\cc ALIA         & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
\cc AUFBVDTLIA   & \cc             & \cc             & {CVC4} *               & {CVC4} *              \\
\cc AUFDTLIA     & \cc             & \cc             & {CVC4} *               & {CVC4}                \\
\cc AUFLIA       & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
\drc
\cc AUFLIRA      & \cc CVC4 {{[}Z3{]}}      & Vampire {{[}Z3{]}}      & Vampire {{[}Z3{]}}             & \cc CVC4 {{[}Z3{]}}            \\
\drc
\cc AUFNIRA      & \cc {CVC4} *    & {Vampire}       & {Vampire}              &\cc  {CVC4}            \\
\cc BV           & \cc CVC4 {{[}Z3{]}} *    & {Q3B}           & Q3B {{[}Z3{]}}             &  \cc {CVC4}               \\
\cc BVFP         & \cc             & \cc             & \cc                    & \cc {CVC4} *          \\
\cc FP           & \cc             & \cc             & \cc                    & \cc {CVC4} *          \\
\cc LIA          & {CVC4}     & {CVC4}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
\cc LRA          & {CVC4}     & {CVC4}     & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
\cc NIA          & \cc CVC4 {{[}Z3{]}} *     & \cc ProB {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
\rc
\cc NRA          & {CVC4} *        & {Vampire}       & {Redlog}               & Vampire {{[}Z3{]}/Vampire}    \\
\cc QF\_ABV      & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
\cc QF\_ABVFP    & \cc             &  \cc            & \cc {---}              & \cc {CVC4}            \\
\cc QF\_ALIA     & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\drc
\cc QF\_ANIA     & CVC4 {{[}Z3{]}} *& {CVC4} *        & {CVC4} *               & CVC4 {{[}Z3{]}} *           \\
\cc QF\_AUFBV    & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}} & Yices2 {{[}MathSAT{]}}        & \cc {CVC4}            \\
\drc
\cc QF\_AUFLIA   & {Yices2}        & {Yices2}        & {Yices2}                 & {Yices2}              \\
\cc QF\_AUFNIA   & {CVC4} *        & {CVC4} *        & CVC4 {{[}Z3{]}} *        & CVC4 {{[}Z3{]}} *     \\
\cc QF\_AX       & {Yices2}        & {Yices2}        & {Yices2}                 & {Yices2}              \\
\drc
\cc QF\_BV       & {Boolector}     & {Boolector}     & {Boolector/MinkeyRink}   & {Boolector/MinkeyRink}\\
\cc QF\_BVFP     & {Z3} *          & {{[}Z3{]}} *    & \cc COLIBRI {{[}Z3{]}} * & \cc {CVC4}            \\
\drc
\cc QF\_DT       & \cc             & \cc             & {CVC4} *               & {CVC4} *              \\
\cc QF\_FP       & \cc {Z3} *      & \cc {{[}MathSAT{]}} * & COLIBRI {{[}Z3{]}}             & {COLIBRI}             \\
\drc
\cc QF\_IDL      & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}} & {Yices2}               & {Yices2}              \\
\cc QF\_LIA      & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}}        & \cc {SPASS-SATT}      \\
\drc
\cc QF\_LIRA     & {Yices2}        & {Yices2}        & Yices2 {{[}Z3{]}}        & Yices2 {{[}Z3{]}}       \\
\cc QF\_LRA      &  {CVC4}         & {CVC4}          & {CVC4}                 & {CVC4}                \\
\cc QF\_NIA      & \cc AProVE {{[}Z3{]}} & \cc Yices2 {{[}Z3{]}} & {CVC4}                 & {CVC4}                \\
\cc QF\_NIRA     & {CVC4}          & {CVC4}          & \dcc {SMT-RAT}         & \dcc {SMT-RAT}        \\
\cc QF\_NRA      & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}}      & {Yices2}      & Yices2 {{[}Z3{]}}        \\
\cc QF\_RDL      & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\cc QF\_SLIA     & \cc             & \cc             & \cc                    & \cc {CVC4} *          \\
\cc QF\_UF       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\drc
\cc QF\_UFBV     & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
\cc QF\_UFIDL    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\cc QF\_UFLIA    & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}} & {Yices2}               & {Yices2}              \\
\cc QF\_UFLRA    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\cc QF\_UFNIA    & \cc {CVC4} *    & {Yices2/CVC4}   & {Yices2}               & {Yices2}              \\
\cc QF\_UFNRA    & \cc CVC3 {{[}Z3{]}} *     & {Yices2}        & Yices2 {{[}Z3{]}}             & {Yices2}              \\
\cc UF           & {CVC4}          & {CVC4}          & \dcc {Vampire}         & \dcc {CVC4/Vampire}   \\
\drc
\cc UFBV         & CVC4 {{[}Z3{]}} *    & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}} *            & CVC4 {{[}Z3{]}} *           \\
\cc UFDT         & \cc             & \cc             & {CVC4} *               & {CVC4}                \\
\rc
\cc UFDTLIA      &                 &                 & {Vampire} *            & {CVC4}                \\
\cc UFIDL        & CVC4 {{[}Z3{]}}  & {CVC4}          & {CVC4}                 & CVC4 {{[}Z3{]}}        \\
\cc UFLIA        & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
\cc UFLRA        & \cc {CVC3}      & \cc Vampire {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
\cc UFNIA        & \cc {CVC4} *    & {Vampire}       & {Vampire}              & Vampire {{[}Z3{]}/Vampire}    \\
\bottomrule
